### 2016-11-21 Paper_v1.tex
Some changes in MM

\subsection*{Sequence specific calculation of carbon yield.}
We estimated the theoretical maximum CAT carbon yield using sequence-specific flux balance analysis (ssFBA) \cite{Allen:2003aa}.
The sequence specific flux balance analysis problem was formulated as:
\begin{equation}
 \begin{multlined}
	\qquad \qquad \qquad \max_{\boldsymbol{w}}{} \! \left( w_{TL} = \mathbf{\boldsymbol{\theta}}^T \boldsymbol{w} \right) \\
	\mathrm{Subject \; to:}
	 \; \; \mathbf{S}\mathbf{w}=\mathbf{0} \\
\alpha_i \leq w_i \leq \beta_i  \qquad i=1,2,\hdots,\mathcal{R}
 \end{multlined}
\end{equation}
where $\mathbf{S}$ denotes the stoichiometric matrix, $\mathbf{w}$ denotes the unknown flux vector, $\boldsymbol{\theta}$ denotes the objective selection vector
and $\alpha_i$ and $\beta_i$ denote the lower and upper bounds on flux $w_{i}$, respectively.
The glucose uptake rate was bounded in the range [0,40 mM/h] according to experimental data;
while the amino acid uptake rates were bounded by [0,30 mM/h], but did not reach the maximum flux.
The transcription and translation rates were modeled using the template reactions:

\begin{eqnarray*}
G_{p}+R_{1} &\longrightarrow& G_{p}^{*} \\
G_{p}^{*}+\sum_{i}\eta_{i}iTP &\longrightarrow& mRNA+G_{p}+R_{1}+2\sum_{i}\eta_{i}P \qquad{i=A,C,G,U}\\
mRNA &\longrightarrow& \sum_{i}\eta_{i}iMP \\
mRNA+R_{2} &\longrightarrow& R_{2}^{*} \\
\alpha_{j}X_{j}+\alpha_{j}tRNA+\alpha_{j}ATP &\longrightarrow& \alpha_{j}XtRNA_{j}+\alpha_{j}AMP+2\alpha_{j}P \qquad{j=1,2,\hdots,20}\\
R_{2}^{*}+\sum_{j}\alpha_{j}\Big(XtRNA_{j}+2GTP\Big) &\longrightarrow& Protein+R_{2}+mRNA\\
&& \quad +\sum_{j}\alpha_{j}\Big(tRNA+2GDP+2P\Big)
\end{eqnarray*}
where $G_{p}$ denotes the gene of protein $p$, $R_{1}$ denotes the concentration of RNA polymerase, $G_{p}^{*}$ denotes the gene bounded by the RNA polymerase, $\eta_{i}$ and $ \alpha_{j}$ denotes the coefficient for species $i$ and $j$ respectively, $P$ denotes phosphate, $R_{2}$ denotes the ribosome concentration, $R_{2}^{*}$ denotes bounded ribosome, and $X_{j}$ denotes the amino acid species $j$.

>>>>

\subsection*{Sequence specific calculation of carbon yield.}
We estimated the theoretical maximum CAT carbon yield using sequence-specific flux balance analysis (ssFBA) \cite{Allen:2003aa}.
The sequence specific flux balance analysis problem was formulated as:
\begin{equation}
 \begin{multlined}
	\qquad \qquad \qquad \max_{\boldsymbol{w}}{} \! \left( w_{TL} = \mathbf{\boldsymbol{\theta}}^T \boldsymbol{w} \right) \\
	\mathrm{Subject \; to:}
	 \; \; \mathbf{S}\mathbf{w}=\mathbf{0} \\
\alpha_i \leq w_i \leq \beta_i  \qquad i=1,2,\hdots,\mathcal{R}
 \end{multlined}
\end{equation}
where $\mathbf{S}$ denotes the stoichiometric matrix, $\mathbf{w}$ denotes the unknown flux vector, $\boldsymbol{\theta}$ denotes the objective selection vector
and $\alpha_i$ and $\beta_i$ denote the lower and upper bounds on flux $w_{i}$, respectively.
The objective of the calculation is the maximization of CAT translation rate, $w_{TL}$.
The total glucose uptake rate was bounded by [0,40 mM/h] according to experimental data;
while the amino acid uptake rates were bounded by [0,30 mM/h], but did not reach the maximum flux.
The transcription and translation rates were modeled using the template reactions:
\begin{eqnarray*}
G_{p}+R_{1} &\longrightarrow& G_{p}^{*} \\
G_{p}^{*}+\sum_{k}\eta_{k}\cdot kTP &\longrightarrow& mRNA+G_{p}+R_{1}+2\sum_{k}\eta_{k}\cdot Pi \qquad{k=A,C,G,U}\\
mRNA &\longrightarrow& \sum_{k}\eta_{k}\cdot kMP \\
mRNA+R_{2} &\longrightarrow& R_{2}^{*} \\
\alpha_{j}\cdot AA_{j}+\alpha_{j}\cdot tRNA+\alpha_{j}\cdot ATP &\longrightarrow& \alpha_{j}\cdot AA_{j}:tRNA_{j}+\alpha_{j}\cdot AMP+2\alpha_{j}\cdot Pi \qquad{j=1,2,\hdots,20}\\
R_{2}^{*}+\sum_{j}\alpha_{j}\cdot \Big(AA_{j}:tRNA_{j}+2\cdot GTP\Big) &\longrightarrow& \mathcal{P}+R_{2}+mRNA+\\
&& \quad +\sum_{j}\alpha_{j}\Big(tRNA+2\cdot GDP+2\cdot Pi\Big)
\end{eqnarray*}
where $G_{p}$ denotes the gene of protein $p$,
$R_{1}$ denotes the concentration of RNA polymerase,
$G_{p}^{*}$ denotes the gene bounded by the RNA polymerase,
$\eta_{i}$ and $ \alpha_{j}$ denote the coefficients for species $i$ and $j$ respectively,
$P_{i}$ denotes inorganic phosphate, $R_{2}$ denotes the ribosome concentration, $R_{2}^{*}$ denotes bounded ribosome, and $X_{j}$ denotes the amino acid species $j$.
